---
title: Describing our ignorance about the life history and demography of Thraupidae family.
author: "Edgar L de Lima"
date: "30/03/2021"
output: html_document
---

# Database construction

1. Defining working directory, loading packages and database.
```{r, message=FALSE}
setwd("C:\\Users\\Edgar\\OneDrive - unb.br\\Doutorado\\CapI\\Analises")
library("tidyverse")
library("openxlsx")
library("readxl")
library("ggpubr")
library("reshape")
```


# Treating and analyzing the database.

1. Loading the Prestonian and Raunkiæran shortfalls database.
```{r}
demo<- read.xlsx("Shortfall_data.xlsx", sheet = 1)
hist<- read.xlsx("Shortfall_data.xlsx", sheet = 2)
View(demo)
View(hist)
```


2. Data for temporal analysis of publications.
```{r}
tdem<- demo%>%select(ID,Year)
tlhist<- hist%>%select(ID,Year)
All<-rbind(tdem,tlhist)

tdem<-tdem%>%group_by(Year)%>%
  distinct(ID, .keep_all = T)
tlhist<-tlhist%>%group_by(Year)%>%
  distinct(ID, .keep_all = T)
All<-All%>%group_by(Year)%>%
  distinct(ID, .keep_all = T)
fall<- data.frame(table(All$Year))
fall[,1]<-as.numeric(as.character(fall$Var1))
View(fall)

```

3. Calculating the total number of articles per year.
```{r}
alldata<- read.xlsx("AllData.xlsx")
ano<- alldata%>%select(PY)%>%table()%>%
  data.frame()
ano[,1]<-as.numeric(as.character(ano$.))
fall$Var1
ano<-ano[ano[,1]>=2003,]
ano<-ano[c(-2,-3,-4),]
temp<- data.frame(fall, ano$Freq)
temp<- mutate(temp, publipad= Freq/ano.Freq)
temp<- mutate(temp, posi = publipad+0.03)
View(temp)
```


3.1. Time series percentage of each shortfall.
```{r}
tdem<- demo%>%select(ID,Year)
tlhist<- hist%>%select(ID,Year)

tdem<-tdem%>%group_by(Year)%>%
  distinct(ID, .keep_all = T)
tlhist<-tlhist%>%group_by(Year)%>%
  distinct(ID, .keep_all = T)
View(tdem)
View(tlhist)
```

3.2. Calculating the total number of articles per year for each shortfall.
```{r}
# Prestonian shortfall
prest<- tdem%>%select(Year)%>%table()%>%
  data.frame()
prest$.<- as.numeric(as.character(prest$.))
colnames(prest)<- c("year", "NStudy")
Npad<-prest$NStudy/ano[ano$.%in% prest$year,2]
prest<- data.frame(prest,Npad)

# Raukerian Shortfall
rauk<- tlhist%>%select(Year)%>%table()%>%
  data.frame()
rauk$.<- as.numeric(as.character(rauk$.))
colnames(rauk)<- c("year", "NStudy")
Npadr<-rauk$NStudy/ano[ano$.%in% rauk$year,2]
rauk<- data.frame(rauk,Npadr)
colnames(rauk)<- c("year", "NStudy", "Npad")

#Total
temp2<-temp[,c(1,2,4)]
colnames(temp2)<- c("year", "NStudy", "Npad")

View(temp2)
View(rauk)
View(prest)
```

3.3. Join tables.
```{r}
pr<- rep(c("Prestonian"),nrow(prest))
ra<- rep(c("Raunkiæran"), nrow(rauk))
to<- rep(c("Total"), nrow(temp))
sh<-c(pr,ra, to)
shorts<- rbind(prest,rauk, temp2)
shorts<- data.frame(sh, shorts)
shorts
```


4. Number of publications per shortfalls.
```{r}
fdem<- data.frame(table(tdem$Year))
flhist<- data.frame(table(tlhist$Year))

fdem[,1]<-as.numeric(as.character(fdem$Var1))
flhist[,1]<-as.numeric(as.character(flhist$Var1))
shortfall<- as.factor(c("Prestonian", "Raunkiæran"))
ns<- c(sum(fdem$Freq),sum(flhist$Freq))
lacunas<- data.frame(shortfall,ns)
View(lacunas)
```

5. Figure with two shortfalls.
```{r, fig.height=8}
ggplot(shorts, aes(x=year, y= Npad, colour= sh))+
  geom_line(size= 1)+
  geom_point(size= 4)+
  scale_x_continuous(limits = c(2003,2020), breaks = seq(2003,2020,1))+
  scale_y_continuous(limits = c(0.0,1), breaks = seq(0.0,1.0,0.1))+
  scale_color_manual(values = c("Prestonian"= "Darkred", "Raunkiæran"="Darkblue", "Total"= "Black"))+
  labs(colour= "Shortfall")+
  ylab("Percentage of studies")+
  xlab("Year")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.title = element_text(size = 20, colour = "black"),axis.text.x = element_text(size = 16, colour = "black"),axis.text.y = element_text(size = 16, colour = "black"), panel.border = element_rect(size= 1.4),
        legend.position = c(0.93,0.93), legend.text = element_text(size= 14), legend.title = element_text(size= 16),
        plot.tag = element_text(size = 20, face = "bold"))

ggsave(filename = "tempseries.tiff", width = 34, 
       height = 25, units = "cm", dpi = 600)

```

6. Number of studies for each parameters of Prestonian shortfall.
Obs: Only parameters that presented one or more studies
```{r}
dem<- demo%>%select(-(Obs:Year),-(ID:Species))
dem<-ifelse(dem[]!= "NA", 1,0)
dem<- replace(x = dem, list = is.na(dem), values = 0)
Species<-demo$Species
dem2<- data.frame(Species, dem)
dem2<-dem2%>%group_by(Species) %>% summarise_each(funs(sum))

sp<- dem2$Species
dem2<- dem2[,-1]
rownames(dem2)<- sp
colnames(dem2)<- colnames(dem)
dem3<- as.matrix(dem2)
Dem<- melt(dem3)
colnames(Dem)<- c("Specie", "Parameter", "Value")

View(Dem)
```

7. Number of studies for each parameters of Raunkiæran shortfall.
Obs: Only parameters that presented one or more studies
```{r}
lhist<- hist%>%select(-(Obs:Year),-(ID:Species))
lhist<-ifelse(lhist[]!= "NA", 1,0)
lhist<- replace(x = lhist, list = is.na(lhist), values = 0)
Species<-hist$Species
lhist2<- data.frame(Species, lhist)
lhist2<-lhist2%>%group_by(Species) %>% summarise_each(funs(sum))

sp<- lhist2$Species
lhist2<- lhist2[,-1]
rownames(lhist2)<- sp
colnames(lhist2)<- colnames(lhist)
lhist3<- as.matrix(lhist2)
Lhist<- melt(lhist3)
colnames(Lhist)<- c("Specie", "Parameter", "Value")

View(Lhist)
```


8. Plot of number of studies for each Raunkiæran shortfall parameter.
```{r}
ggplot(Lhist, aes(y = Parameter, x = Specie, fill = Value)) +
  geom_tile(color = "black") +
  geom_text(aes(label = Value), color = "white", size = 4.5) +
  labs( title = "Raunkiæran Shortfall", x= "Species",
       y= "Parameters")+
  coord_fixed()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        axis.title = element_text(size = 25, colour = "black"),
        axis.text = element_text(size= 16, colour = "black"),
        plot.title = element_text(hjust = 0.5, color = "Black", size = 20),
        legend.position = "none")

ggsave(filename = "StLifeHist.tiff", width = 50, 
        height = 30, units = "cm", dpi = 600)
```

9. Plot of number of studies for each Prestonian shortfall parameter.
```{r}
ggplot(Dem, aes(y = Parameter, x = Specie, fill = Value)) +
  geom_tile(color = "black") +
  geom_text(aes(label = Value), color = "white", size = 4.5, face= "bold") +
  labs( title = "Prestonian Shortfall", x= "Species",
       y= "Parameters")+
  coord_fixed()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        axis.title = element_text(size = 20, colour = "black"),
        axis.text = element_text(size= 14, colour = "black"),
        plot.title = element_text(hjust = 0.5, color = "Black", size = 20),
        legend.position = "none")

ggsave(filename = "Stdemography.tiff", width = 25, 
       height = 25, units = "cm", dpi = 600)
```


10. Frequence of parameters per species for Prestonian shortfal.
```{r}
dem2<-demo%>%group_by(Species)%>%
  distinct(ID, .keep_all = T)%>%
  arrange(Species)%>%select(-(Obs:Year),-(ID))

dem3<-as.data.frame(ifelse(dem2[]!= "NA", 1,0))
dem3[,1]<- dem2[,1]
dem3<-dem3%>%replace(is.na(.), 0)%>%
    group_by(Species)%>%
    summarise_all(funs(sum))
dem4<- dem3[,2:ncol(dem3)]!=0
dem4<-replace(dem4,dem4,1)
dem4<- rowSums(dem4)
demcont<- data.frame(dem3$Species,dem4)
colnames(demcont)<-c("Species","Param")
View(demcont)
```

11. Frequence plot of parameters per species for Prestonian shortfal.
```{r}
b<-ggplot(demcont, aes(x = Param)) +
  geom_histogram(fill = "Black", colour= "white",size= .3, binwidth = 1)+
  scale_x_continuous(breaks= seq(0,10,1),
                   limits = c(0,10))+
  scale_y_continuous(breaks= seq(0,30,2),
                     limits = c(0,30))+
    
  xlab("Number of parameters") + 
  #ylab("Number of species")+
  ggtitle("Prestonian shortfall",)+
  labs(tag = "b)")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.title.x= element_text(size = 16, colour = "black"),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 16, colour = "black"),
        panel.border = element_rect(size= 1.4),
        plot.title  = element_text(size = 20, 
                                   hjust = .5),
        plot.tag = element_text(size = 20, face = "bold"))

ggsave(filename = "Spdem.tiff", width = 31, 
        height = 25, units = "cm", dpi = 600)

```

12. Frequence of parameters per species for Raunkiæran shortfal.
```{r}
lhist2<-hist%>%group_by(Species)%>%
  distinct(ID, .keep_all = T)%>%
  arrange(Species)%>%select(-(Obs:Year),-(ID))
View(lhist2)

lhist3<-as.data.frame(ifelse(lhist2[]!= "NA", 1,0))
lhist3[,1]<- lhist2[,1]
View(lhist3)
lhist3<-lhist3%>%replace(is.na(.), 0)%>%
    group_by(Species)%>%
    summarise_all(funs(sum))
lhist4<- lhist3[,2:ncol(lhist3)]!=0
lhist4<-replace(lhist4,lhist4,1)
lhist4<- rowSums(lhist4)
lhistcont<- data.frame(lhist3$Species,lhist4)
colnames(lhistcont)<-c("Species","Param")
View(lhistcont)

```

13. Frequence plot of parameters per species for Raunkiæran shortfal.
```{r}
a<-ggplot(lhistcont, aes(x = Param)) +
  geom_histogram(fill = "Black", colour= "white", size= .3, binwidth =1)+
 scale_x_continuous(breaks= seq(0,24,2),
                   limits = c(0,24))+
  scale_y_continuous(breaks= seq(0,30,2),
                     limits = c(0,30))+
  ggtitle("Raunkiæran shortfall")+
  labs(tag = "a)")  +
  xlab("Number of parameters") + 
  ylab("Number of species")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.title = element_text(size = 16, colour = "black"),
        axis.text = element_text(size = 16, colour = "black"),
        panel.border = element_rect(size= 1.4),
        plot.title  = element_text(size = 20, 
                                   hjust = .5),
        plot.tag = element_text(size = 20, face = "bold"))

ggsave(filename = "sphist.tiff", width = 31, 
        height = 25, units = "cm", dpi = 600)

```

14. Joining the plots of Raunkiæran and Prestonian shortfalls.
```{r}
ggarrange(a,b,ncol = 2, nrow = 1)

ggsave(filename = "spst.tiff", width = 34, 
       height = 25, units = "cm", dpi = 600)
```

15. Frequency of studies by species for clutch size and variation.
```{r}
cs<-demo%>%group_by(Species)%>%
  distinct(ID, .keep_all = T)%>%
  arrange(Species)%>%select("ClutchSize", "ClutchSize(SE)","ClutchSize(max)" )
 cs[which(cs$`ClutchSize(max)`>=0),3]<-1 
View(cs)

cs2<-as.data.frame(ifelse(cs[]!= "NA", 1,0))
cs2[,1]<- cs[,1]
View(cs2)

cs2<-cs2%>%replace(is.na(.), 0)%>%
    group_by(Species)%>%
    summarise_all(funs(sum))
View(cs2)

param1<- rep(c("Clutch size"), nrow(cs2))  
param2<- rep(c("Clutch size variation"), nrow(cs2))
s<-data.frame(param1, cs2$ClutchSize)
v<-data.frame(param2, cs2$`ClutchSize(SE)`)
colnames(s)<- c("Param", "Fsp")
colnames(v)<- c("Param", "Fsp")
cs3<-bind_rows(s,v)
cs3<- cs3%>%filter(Fsp!=0)
View(cs3)

```

16. Frequency plot of studies by species for clutch size and variation.
```{r}
ab<-ggplot(cs3, aes(x = Fsp, fill= Param, colour= Param)) +
  geom_histogram( size= .3, position = "dodge",bins = 10)+
 scale_color_manual(values = c("darkred", "darkblue"),
                    aesthetics = c("colour", "fill"))+
  
  scale_x_continuous(breaks= seq(1,2,1),
                     limits = c(0.85,2.1))+
  scale_y_continuous(breaks= seq(0,34,2),
                     limits = c(0,34))+
  ggtitle("Prestonian shortfall")+
  labs(tag = "b)")+  
  xlab("Number of studies") + 
  ylab("Number of species")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.title.x = element_text(size = 16, colour = "black"),
        axis.text = element_text(size = 16, colour = "black"),
        axis.title.y = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.position = c(0.75,0.9),
        panel.border = element_rect(size= 1.4),
        plot.title  = element_text(size = 20, 
                                   hjust = .5),
        plot.tag = element_text(size = 20, face = "bold"))
  
  #ggsave(filename = "spsize.tiff", width = 31, 
   #     height = 25, units = "cm", dpi = 600)

```


17. Frequency of studies by species for body mass and variation.
```{r}
bm<-hist%>%group_by(Species)%>%
  distinct(ID, .keep_all = T)%>%
  arrange(Species)%>%select("BodyMass", "BodyMass(SE)","BodyMass(max)" )
 bm[which(bm$`BodyMass(max)`>=0),3]<-1 
View(bm)

bm2<-as.data.frame(ifelse(bm[]!= "NA", 1,0))
bm2[,1]<- bm[,1]
View(bm2)

bm2<-bm2%>%replace(is.na(.), 0)%>%
    group_by(Species)%>%
    summarise_all(funs(sum))
View(bm2)

param1<- rep(c("Body Mass"), nrow(bm2))  
param2<- rep(c("Body Mass variation"), nrow(bm2))
s<-data.frame(param1, bm2$BodyMass)
v<-data.frame(param2, bm2$`BodyMass(SE)`)
colnames(s)<- c("Param", "Fsp")
colnames(v)<- c("Param", "Fsp")
bm3<-bind_rows(s,v)
bm3<- bm3%>% filter(Fsp!=0)
View(bm3)
```


18. Frequency plot of studies by species for clutch size and variation.
```{r}
bb<-ggplot(bm3, aes(x = Fsp, fill= Param, colour= Param)) +
  geom_histogram( size= .3, position = "dodge",bins = 10)+
 scale_color_manual(values = c("darkred", "darkblue"),
                    aesthetics = c("colour", "fill"))+
  
  scale_x_continuous(breaks= seq(1,3,1),
                     limits = c(0.85,3.20))+
  scale_y_continuous(breaks= seq(0,34,2),
                     limits = c(0,34))+
  ggtitle("Raunkiæran shortfall")+
  labs(tag = "a)")+
  xlab("Number of studies") + 
  ylab("Number of species")+
  theme_bw()+
  
  theme(panel.grid = element_blank(),
        axis.title = element_text(size = 16, colour = "black"),
        axis.text = element_text(size = 16, colour = "black"),legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.position = c(0.7,0.9),
        panel.border = element_rect(size= 1.4),
        plot.title  = element_text(size = 20, 
                                   hjust = .5),
        plot.tag = element_text(size = 20, face = "bold"))
  
#ggsave(filename = "SpBSize.tiff", width = 31, 
 #       height = 25, units = "cm", dpi = 600)

```

19. Joining the plots body mass and clutch size.
```{r}
ggarrange(bb,ab,ncol = 2, nrow = 1)
ggsave(filename = "spcbsize.tiff", width = 36, 
       height = 25, units = "cm", dpi = 600)
```


20. Proportion of parameters without at least one study.
```{r}
gaphist<-hist%>%group_by(Species)%>%
  distinct(ID, .keep_all = T)%>%
  arrange(Species)%>%select(-(Obs:Year),-(ID))

gaphist<-as.data.frame(ifelse(gaphist[]!= "NA", 1,0))
gaphist<-gaphist%>%replace(is.na(.), 0)
totalhist<- ncol(gaphist[,-1])
soma1<-colSums(gaphist)
szero<-length(soma1[soma1[]==0])
rhist<- szero/totalhist

gapdem<-demo%>%group_by(Species)%>%
  distinct(ID, .keep_all = T)%>%
  arrange(Species)%>%select(-(Obs:Year),-(ID))

gapdem<-as.data.frame(ifelse(gapdem[]!= "NA", 1,0))
gapdem<-gapdem%>%replace(is.na(.), 0)

totaldem<- ncol(gapdem[,-1])
soma2<-colSums(gapdem)
szero<-length(soma2[soma2[]==0])
rdem<- szero/totaldem

gap<- c("Prestonian","Raunkiæran" )
perc<- c(rhist,rdem)
perc2<- data.frame(gap,perc)
View(perc2)
```

# Data analysis of the relationship between body size and number of studies.

1. Calculating the body size mean and number of studies by gender.
```{r}
hist2<- hist%>%select(ID,Species,BodyMass)%>% replace(is.na(.), 0)
 genero<-hist2$Species%>%
   str_split(" ", n=2, simplify = T)
  hist2[,2]<-genero[,1]
  
bodymean<- hist2%>% group_by(Species)%>%
   summarise(BodyMean= mean(BodyMass))

bodymean<- bodymean%>% filter(BodyMean!= 0)
demo2<- demo%>%select(ID,Species)

genero<-demo2$Species%>%
   str_split(" ", n=2, simplify = T)
  demo2[,2]<-genero[,1]

 demo3<-demo2%>%
    filter(Species== "Anisognathus"|Species== "Chalcothraupis"|Species== "Conothraupis"|Species== "Diglossa"|Species== "Donacospiza"|Species== "Gubernatrix"|Species== "Ixothraupis"|Species== "Paroaria"|Species== "Schistochlamys"|Species== "Sporophila"|Species== "Stilpnia"|Species== "Tangara"|Species== "Thlypopsis"|Species== "Thraupis" )

  
 hist3<- hist2[,-3]
 
 dh<-rbind(demo3, hist3)

num<-dh%>%distinct(ID,Species, .keep_all = T)%>% select(Species)
nstud<-as.data.frame(table(num))

nstud2<-nstud%>%
    filter(num== "Anisognathus"|num== "Chalcothraupis"|num== "Conothraupis"|num== "Diglossa"|num== "Donacospiza"|num== "Gubernatrix"|num== "Ixothraupis"|num== "Paroaria"|num== "Schistochlamys"|num== "Sporophila"|num== "Stilpnia"|num== "Tangara"|num== "Thlypopsis"|num== "Thraupis" )

bodymean[,3]<- nstud2$Freq
colnames(bodymean)<-c("Genus", "BodyMean", "Nstud")
View(bodymean)
```

2. Loading packages for fit non-linear regression.
```{r}
library(lattice)
library(latticeExtra)
library(nlme)
library(minpack.lm)
library(nls2)
library(openxlsx)
library(nlstools)
```

3. Fiting non-linear regression with Gompertz equation. 
```{r}
# Gompertz equation
#model<-nlsLM(bodymean$Nstud~a*bodymean$BodyMean^-b,
 #            start=list(a=100,b=0.000004),data = bodymean,
  #     alg="default")

model2<- nls(bodymean$Nstud ~ a*bodymean$BodyMean^b,
             start=list(a=0.1,b=0.00004), data = bodymean)
model2
result<-summary(model2)
Regres<-data.frame(result$coefficients)

write.xlsx(Regres,"Result.xlsx" )
```

4. Plot of relationship between body mean mass and number of studies.
```{r}
ggplot(bodymean,aes(x=BodyMean, y= Nstud))+
 geom_point(size= 3.5)+
  stat_smooth(method = "nls",
              formula = y ~ a*x^-b,
              method.args = list(start = list(a=0.1,b=0.00004)),
              se = F, colour= "red")+
  scale_x_continuous(breaks= seq(0,50,5),
                    limits = c(0,50))+
  scale_y_continuous(breaks= seq(0,24,2),
                     limits = c(0, 24))+
  xlab("Body mean mass (g)") + 
  ylab("Number of studies")+
  annotate("text",y= 24, x= 40 ,label="t= -1.413; df= 12; p= 0.183", size= 8)+
  annotate("text",y= 22.5, x= 36 ,label="y== 14.05*x^{-0.52} ",parse= T, size= 8)+
  annotate("text",y= 22, x= 8 ,label= "Sporophila", 
           size= 8, fontface="italic")+
  annotate("text",y= 0.3, x= 47 ,label= "Gubernatrix", 
           size= 8, fontface="italic")+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.title = element_text(size = 20, colour = "black"),
        axis.text = element_text(size = 16, colour = "black"),
        panel.border = element_rect(size= 1.4))
ggsave(filename = "Reg2.tiff", width = 31, 
        height = 25, units = "cm", dpi = 600)


```

# Analysis of relationship between studies parameters and phylogeny.


1. Building dataset for analysis.
```{r}
demo<- demo%>% select(-(Obs:Year))
hist<- hist%>% select(-(Obs:Year))

dem<-demo%>%arrange(Species)%>%replace(is.na(.), 0)
his<- hist%>%arrange(Species)%>% replace(is.na(.), 0)
dem[,c(3:ncol(dem))]<- ifelse(dem[,c(3:ncol(dem))] > 0, 1,0)
his[,c(3:ncol(his))]<- ifelse(his[,c(3:ncol(his))] > 0, 1,0)
View(dem)
View(his)
```

```{r}
dem2<- dem%>%group_by(Species)%>%
  distinct(ID, .keep_all = T)

his2<- his%>%group_by(Species)%>%
  distinct(ID, .keep_all = T)
View(dem2)
dem3<-by(dem2[,3:ncol(dem2)],INDICES = as.factor(dem2$Species), FUN= colSums)

his3<-by(his2[,3:ncol(his2)],INDICES = as.factor(his2$Species), FUN= colSums)
```

2. Function for build presence-absence table.
```{r}
pu<- function(x){
  Ncol<-length(names(x))+1
  Nlin<-length(x[[1]])
  tabela<- as.data.frame(matrix(nrow = Nlin, ncol = Ncol))
  tabela[,1]<- names(x[[1]])
  colnames(tabela)<- c("Param",names(x))
  
  for (i in 1:length(names(x))) {
      tabela[,i+1]<- x[[i]]
  }
  cnames<- c("Param", tabela[,1])
  tab<- t(tabela)
  tab<-data.frame(names(x),tab[-1,])
  colnames(tab)<-cnames
  return(tab)
}
```

3. Creating and saving presence-absence tables.
```{r}
dem4<-pu(dem3); View(dem4)
his4<-pu(his3); View(his4)
write.xlsx(dem4, "dempa.xlsx")
write.xlsx(his4, "histpa.xlsx")
```

4. Loading data.
```{r}
#setwd("C:\\Users\\Edgar\\OneDrive - unb.br\\Doutorado\\CapI\\Dados_analises")
#library(ape);library(picante);library(phytools)

#dados<-read.xlsx("DadosEstudos.xlsx", sheet = 1)
#traup<-read.tree("phy_cons.txt")

traup$tip.label<-traup$tip.label%>%
  str_replace_all("_"," ")
```

5. Altering Species names
```{r}
a<- !dados$Param %in% traup$tip.label

repl<-c("Tiaris bicolor","Poospiza thoracica","Tangara ruficervix","Tangara guttata","Tangara rufigula","Saltator atricollis","Oryzoborus angolensis","Oryzoborus maximiliani","Tangara cayana","Tangara cyanicollis", "Tangara vitriolina", "Oreomanes fraseri")
b<-dados$Param[a]
b<-b[- c(8,9,10,11)]

for(i in 1:length(b)){
  traup$tip.label[which(traup$tip.label== repl[i])]<-b[i]
}
 write.tree(traup,"phy_cons.txt" )
```


6. Selecinando na filogenia apenas as espécies do banco de dados
```{r}
 traup$tip.label<-traup$tip.label%>%str_replace_all("_"," ")
c<-dados$Param %in% traup$tip.label
c2<- dados$Param[c]
dados2<-dados%>%filter(Param%in%c2)

retirar<-!traup$tip.label%in%dados$Param
ret2<-traup$tip.label[retirar]
traup<-drop.tip(traup, ret2)
traup$tip.label
 write.tree(traup,"phyThraup.txt" )
 
```

7. 
```{r}
# Calculando matriz de distnacia dos parametros
dist.trait <- as.matrix(dist(dados2[,-1]))

# Distancia filogenética
dist.tree <- cophenetic(traup)

# Calcula o Mantel e simula um modelo nulo para o teste de hipótese
Mantel <- mantel(dist.trait, dist.tree, permutation = 10000)
Mantel

```
